Puyuma: Linux-based RTOS experimental platform for constructing self-driving miniature vehicles

### 2017-05-15 cthpc-2017/paper.tex
Mention further improvements about OpenCV

\begin{table}[]
\centering
\caption{Maximum latency for Xenomai}
\label{xeno_compare}
\begin{tabular}{llll}
                              & User task & Kernel task & Irq task \\
Xenomai with original kernel  & 76.067 us & 36.262 us   & 27.895us \\
Xenomai with customized kernel & 42.678us  & 29.973us    & 27.11us 
\end{tabular}
\end{table}

@@

The current state lane detector is implemented under OpenCV 2.4 and using single CPU core without GPU acceleration, further hardware optimization like: NEON, Intel TBB may help to speed up the overall performance.

@@

>>>>

\begin{table}[]
\centering
\caption{Maximum latency for Xenomai}
\label{xeno_compare}
\begin{tabular}{llll}
                              & User task & Kernel task & IRQ task \\
Xenomai with original kernel  & 76.067 us & 36.262 us   & 27.895us \\
Xenomai with customized kernel & 42.678us  & 29.973us    & 27.11us 
\end{tabular}
\end{table}

@@

At present, the algorithms of lane detector is implemented by using with OpenCV version 2.4 as single-threaded task without specified CPU or GPU accelerations but yet leads to reasonaly fast response time while collaboring to ROS framework as Table \ref{lane_detector_condition} indicates.

@@

It is possible to build 30\% faster OpenCV packages \cite{faster-opencv} optimized for Raspberry Pi 3 via ARM's advanced SIMD instruction \cite{arm-neon} and Intel's Threading Building Blocks \cite{intel-tbb} where the whole lane detector can be accelerated with code modifications.
